---
title: "Coursera Data Science"
author: "José Manuel Coca"
date: '2022-04-27'
output: html_document
---

# R-Programming
## Week 1 Quiz

### **11.** Use the [Week 1 Quiz Data Set](https://d396qusza40orc.cloudfront.net/rprog/data/quiz1_data.zip) to answer questions 11-20. In the dataset provided for this Quiz, what are the column names of the dataset? 

```{r}
hw1_data <- read.csv("C:/Users/Hola/coursera/tasks/course2/hw1_data.csv")
```
```{r}
colnames(hw1_data)
```

### **12.** Extract the first 2 rows of the data frame and print them to the console. What does the output look like?

```{r}
head(hw1_data,2)
```

### **13.** How many observations (i.e. rows) are in this data frame?
```{r}
nrow(hw1_data)
```
Or using the "str" function
```{r}
str(hw1_data)
```

### **14.** Extract the last 2 rows of the data frame and print them to the console. What does the output look like?

```{r}
tail(hw1_data,2)
```

### **15.** What is the value of Ozone in the 47th row?
```{r}
hw1_data[47,"Ozone"]
```

### **16.** How many missing values are in the Ozone column of this data frame?
```{r}
sum(is.na(hw1_data$Ozone))
```

### **17.** What is the mean of the Ozone column in this dataset? Exclude missing values (coded as NA) from this calculation.
```{r}
mean(hw1_data$Ozone, na.rm=TRUE)
```

### **18.** Extract the subset of rows of the data frame where Ozone values are above 31 and Temp values are above 90. What is the mean of Solar.R in this subset?
```{r}
sub1<- subset(hw1_data,Ozone>31&Temp>90)
mean(sub1$Solar.R)
```

### **19.** What is the mean of "Temp" when "Month" is equal to 6? 
```{r}
sub2<-subset(hw1_data,Month==6)
mean(sub2$Temp)
```

### **20.** What was the maximum ozone value in the month of May (i.e. Month is equal to 5)?
```{r}
sub3<-subset(hw1_data,Month==5)
max(sub3$Ozone, na.rm = TRUE)
```

